Methodology for Assessing the State of the Practice for Domain X

### 2020-09-20 StateOfPractice/Methodology/Methodology.tex
updated section 3 of Methodology doc

@@

\section{Overview of Steps in Assessing Quality of the Domain Software}

\begin{enumerate}
\item Start with state of practice research questions. (Section~\ref{ResearchQuestions}) \pmi{To be completed; should I remove section 2 from above and just link to ../OverallResearchProposal/ObjectivesAndResearchQuestions.pdf?, move the doc to this folder?}
\item Identify the domain. (Section~\ref{SecIdentifyDomain}) \pmi{To be reviewed}
\item \emph{Domain Experts}: Create a top ten list of software packages in the domain. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Brief the Domain Experts on the overall objective, research proposal, research questions, measurement template, survey for short list projects, usability tests, performance benchmarks, maintainability experiments. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Identify broad list of candidate software packages in the domain. (Section~\ref{SecIdentifyCandSoft}) \pmi{To be reviewed}
\item Preliminary filter of software packages list. (Section~\ref{SecInitialFilter}) \pmi{To be reviewed}
\item \emph{Domain Experts}: Review domain software list. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Domain Analysis. (Section~\ref{SecDomainAnalysis})\pmi{To be reviewed}
\item \emph{Domain Experts}: Vet domain analysis. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts}) \pmi{This was part of the original Steps in Assessing Quality list. We need to add it to the Meeting Agenda}
\item Gather source code and documentation for each prospective software package.
\item Collect empirical measures. (Section~\ref{SecEmpiricalMeasures}) \pmi{To be completed - go over how to clean this up in meeting, or through an issue}
\item Measure using ``shallow'' measurement template. (Section~\ref{SecShallowMeasure}) \pmi{To be reviewed}
\item Use AHP process to rank the software packages. (Section~\ref{SecAHP}) \pmi{To be reviewed}
\item Identify a short list of top software packages, typically four to six, for deeper exploration according to the AHP rankings of the shallow measurements.
\item \emph{Domain Experts}: Vet AHP ranking and short list. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts}) \pmi{This was part of the original Steps in Assessing Quality list. We need to add it to the Meeting Agenda}
\item With short list:
\begin{enumerate}
\item Survey developers (\href{run:Questions to Developers.pdf}{Questions to Developers})
\item Usability experiments (\href{run:User Experiments.pdf}{User Experiments})
\item Performance benchmarks\pmi{note: this is still in consideration}
\item Maintainability experiments\pmi{note: this is still in consideration}
\end{enumerate}
\item Rank short list. (Section~\ref{SecRankShortList}) \pmi{To be completed; how will we do this? status of usability experiments?}
\item Document answers for research questions.
\end{enumerate}

@@

\section{Measure Using Shallow Measurement Template} \label{SecShallowMeasure}
For each software package fill out one column in the \href{run:Combined_MeasurementTemplate_EmpiricalMeasures.xlsx}{Measurement Template} following these steps:
\ad{Maybe a one or two sentences introduction to the template?}
\begin{enumerate}
	\item Gather the summary information for rows 3 to 20
	\item Using the GitStats tool found in Section \ref{gitstats} gather the measurements for rows 105 to 112
	\ad{Will it be easier to use the section names instead of row numbers? Otherwise it can be hard to maintain.}
	\item Using the SCC tool found in Section \ref{scc} gather the measurements for rows 114 to 118
	\item If the software package is found on git, gather the measurements for rows 120 to 124
	\item Review installation documentation and attempt to install the software package
	\item Gather the measurements for rows 22 to 37
	\item Gather the measurements for correctness and verifiability in rows 39 to 48
	\ad{for 7 to 14, maybe we can put them together, to something like "measurements for the followings sections..."}
	\item Gather the measurements for surface reliability in rows 50 to 56
	\item Gather the measurements for surface robustness in rows 58 to 61
	\item Gather the measurements for surface usability in rows 63 to 68
	\item Gather the measurements for maintainability in rows 70 to 78
	\item Gather the measurements for reusability in rows 80 to 83
	\item Gather the measurements for surface understandability in rows 85 to 94
	\item Gather the measurements for visibility and transparency in rows 96 to 101
\end{enumerate}

@@

>>>>

Note the following formatting conventions of this document. Red text denotes a link to information within the document. Purple text denotes a link to supplementary information that is external to this document.\pmi{needs to be added to intro to explain convention}

@@

\section{Overview of Steps in Assessing Quality of the Domain Software}\label{StepsAQDS}

\begin{enumerate}
\item Start with state of practice research questions. (Section~\ref{ResearchQuestions}) \pmi{To be completed}
\item Identify the domain. (Section~\ref{SecIdentifyDomain}) \pmi{To be reviewed}
\item \emph{Domain Experts}: Create a top ten list of software packages in the domain. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Brief the Domain Experts on the overall objective, research proposal, research questions, measurement template, survey for short list projects, usability tests, performance benchmarks, maintainability experiments. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Identify broad list of candidate software packages in the domain. (Section~\ref{SecIdentifyCandSoft}) \pmi{To be reviewed}
\item Preliminary filter of software packages list. (Section~\ref{SecInitialFilter}) \pmi{To be reviewed}
\item \emph{Domain Experts}: Review domain software list. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Domain Analysis. (Section~\ref{SecDomainAnalysis})\pmi{To be reviewed}
\item \emph{Domain Experts}: Vet domain analysis. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts}) \pmi{This was part of the original Steps in Assessing Quality list. We need to add it to the Meeting Agenda}
\item Gather source code and documentation for each prospective software package.
\item Collect empirical measures. (Section~\ref{SecEmpiricalMeasures}) \pmi{To be completed - go over how to clean this up in meeting, or through an issue}
\item Measure using measurement template. (Section~\ref{SecShallowMeasure}) \pmi{To be reviewed}
\item Use AHP process to rank the software packages. (Section~\ref{SecAHP}) \pmi{To be reviewed}
\item Identify a short list of top software packages, typically four to six, for deeper exploration according to the AHP rankings of the measurements.
\item \emph{Domain Experts}: Vet AHP ranking and short list. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item With short list:
\begin{enumerate}
\item Survey developers (\href{run:Questions to Developers.pdf}{Questions to Developers})
\item Usability experiments (\href{run:User Experiments.pdf}{User Experiments})
\item Performance benchmarks\pmi{note: this is still in consideration}
\item Maintainability experiments\pmi{note: these experiments need to be completed - to be discussed at next meeting}
\end{enumerate}
\item Rank short list. (Section~\ref{SecRankShortList}) \pmi{To be completed}
\item Document answers for research questions.
\end{enumerate}

@@

\section{Measure Using Measurement Template} \label{SecShallowMeasure}
For each software package fill out one column in the \href{run:Combined_MeasurementTemplate_EmpiricalMeasures.xlsx}{Measurement Template} following these steps:
\ad{Maybe a one or two sentences introduction to the template?}
\begin{enumerate}
	\item Gather the summary information for rows 3 to 20
	\item Using the GitStats tool found in Section \ref{gitstats} gather the measurements for rows 105 to 112
	\ad{Will it be easier to use the section names instead of row numbers? Otherwise it can be hard to maintain.}
	\item Using the SCC tool found in Section \ref{scc} gather the measurements for rows 114 to 118
	\item If the software package is found on git, gather the measurements for rows 120 to 124
	\item Review installation documentation and attempt to install the software package
	\item Gather the measurements for rows 22 to 37
	\item Gather the measurements for correctness and verifiability in rows 39 to 48
	\ad{for 7 to 14, maybe we can put them together, to something like "measurements for the followings sections..."}
	\item Gather the measurements for surface reliability in rows 50 to 56
	\item Gather the measurements for surface robustness in rows 58 to 61
	\item Gather the measurements for surface usability in rows 63 to 68
	\item Gather the measurements for maintainability in rows 70 to 78
	\item Gather the measurements for reusability in rows 80 to 83
	\item Gather the measurements for surface understandability in rows 85 to 94
	\item Gather the measurements for visibility and transparency in rows 96 to 101
\end{enumerate}

@@

\pmi{SS: let's ask the people that do the usability/performance/maintainability experiments to do an AHP pair-wise comparison between the short-list software packages}
